%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{WORK EXPERIENCE}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {System Architect{\enskip\cdotp\enskip}Tech Leader} % Job title
    {Hangzhou Langmy Technology Corporation Ltd} % Organization
    {Hangzhou} % Location
    {2018.12 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead the development of SaaS platform targeting Automobile Parking and Smart Community.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Job title
    {Hangzhou EagleGuard Technology Corporation Ltd} % Organization
    {Hangzhou} % Location
    {2016.9 - 2018.12} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of design and development of software system of anti-uav product, which consists of radar, optical/infrared camera and electromagnetic jammer. The technology we are using includes C++, nodejs, zeromq, cuda, opengl, sql database etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Kingsoft Corporation Ltd} % Organization
    {Chendu} % Location
    {2013.6 - 2016.9} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of designing and developing state-of-the-art game servers with features such as exceptional scalability, excellent reliability and remarkable performance. The technologies used in the project includes C/C++, golang, Lua and shell script programming languages, and also databases such as MySQL, MongoDB and Redis. The whole system runs on Ubuntu 12.04 LTS distributions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Huawei Technologies Corporation Ltd} % Organization
    {Chendu} % Location
    {2010.12 - 2013.6} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in the research and development of company's next gen NAS storage prototype. The system made heavy reference to ZFS file system. I was in charge of design and development the Posix Adaptor Layer module (aka PAL), whose job is interpreting posix-compliant file system requests from Linux's VFS subsystem.}
        \item {Participated in the design of company's large scale distributed storage system. The system inherited PAL module from previous NAS prototype. I was in charge of enhancing PAL module with following concerns: 1) add NFS/CIFS support; 2) add iSCSI support. In addition to PAL's enhancements, I also designed first draft for event-based-io model(simillar to how nodejs works nowadays), whose purpose is to optimally utilize limited number of kernel threads to complete file/disk io.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Storage Software Engineer} % Job title
    {United Information Technology Corporation Ltd} % Organization
    {Shenzhen} % Location
    {2009.7 - 2010.12} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in the development of company's SAN storage product. In charge of maintaining and improving RAID module.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
